Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-30 ms.tex
this and that.

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
  \hline
  {Variable} & {Definition} \\
  \hline
  $M_{\bullet}$ & black hole mass \\
  $\tilde{v}_{w}$ & total heating parameter, including minimum heating
  rate from stellar and black hole velocity dispersion \\
  $v_{w}$ & total heating parameter, excluding minimum heating rate from
  velocity dispersion \\
  $\sigma_{\bullet}$ & The line of sight velocity dispersion from the  $\Mbh-\sigma$ relation (eq.~\eqref{eq:Msigma})\\
  $\sigma_0$ & stellar velocity dispersion (assumed to be radially
  constant and equal to $\sqrt{3} \Mbh$).\\
  $\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
  $r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
  $r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
  $r_{\rm b}$ & outer break radius of stellar density profile \\ 
  $r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
  $\rho_{\star}(r)$ & 3D radial stellar density profile \\
  $\rho(r)$ & gas density of CNM \\
  $M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
  $M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
  $q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
  $\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
  $\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
  $\Gamma$ & power-law slope of radial stellar surface brightness
  profile interior to the break radius \\
  $\delta$ & power-law slope of the 3D stellar density profile inside of
  the break radius, $\delta \equiv \Gamma+1$.\\
  $\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
  $\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
  $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
  $\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
  $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
  $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
  $t_{\rm h}$ & Hubble timescale \\
  $\nu$ & gas density power-law slope at the stagnation radius
  (eq.~[\ref{eq:densSlope}]) \\
  \hline
\label{table:definitions}  
\end{tabular}
%\begin{tablenotes}
%\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}): stellar
  wind heating ({\it orange}), Ia supernovae ({\it green}),
  millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
  Each heating source varies with black hole mass $\Mbh$ calculated
  for average SFHs from \citet{MosterNaab+:2013a}; see
  Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
  v_{w}^{2}$) from the top panel to the radiative cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter
  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star SFHs
  from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
  stagnation radius as a function of $\Mbh$ (green), and the ratio of
  $\zeta/\zeta_{c}$ (purple), where $\zeta_c$
  (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta
  \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are
  impossible.  The latter quantity is calculated for core
  ($\Gamma=0.1$) galaxies  using mean scaling
  relations for $r_b$, $\rinf$, and $\Gamma$ from the
  \citet{LauerFaber+:2007a} galaxy sample.}

 % $\Gamma=0.3
 %  \Mbheight^{-0.24}$, $\rinf=14 \Mbheight^{0.6}$ pc
 %  (eq~\eqref{\eqref{eq:rsoi}}), $\rb\simeq 106 \Mbheight^{0.39} $ pc
 %  (for $\Gamma<0.3$), and $\rb\simeq 100$ pc (for $\Gamma\geq 0.3$)
 %  {\bf Added zeta/zeta_c line but unfortunately caption became
 %    somewhat verbose (I don't think all of this description is
 %    necessary--maybe just say we use scaling relations based on Lauer
 %    et al. sample?) Also being so close to zeta/zeta_c=1 implies
 %    there is a limit to how much scatter we could explain just by
 %    variations in the heating rate}.

\end{figure}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
  \hline
  {Variable} & {Definition} \\
  \hline
  $M_{\bullet}$ & black hole mass \\
  $\tilde{v}_{w}$ & total heating parameter, including minimum heating
  rate from stellar and black hole velocity dispersion \\
  $v_{w}$ & total heating parameter, excluding minimum heating rate from
  velocity dispersion \\
   $\sigma_0$ & stellar velocity dispersion (assumed to be radially
   constant).\\
  $\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
  $r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
  $r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
  $r_{\rm b}$ & outer break radius of stellar density profile \\ 
  $r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
  $\rho_{\star}(r)$ & 3D radial stellar density profile \\
  $\rho(r)$ & gas density of CNM \\
  $M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
  $M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
  $q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
  $\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
  $\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
  $\Gamma$ & power-law slope of radial stellar surface brightness
  profile interior to the break radius \\
  $\delta$ & power-law slope of the 3D stellar density profile inside of
  the break radius, $\delta \equiv \Gamma+1$.\\
  $\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
  $\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
  $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
  $\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
  $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
  $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
  $t_{\rm h}$ & Hubble timescale \\
  $\nu$ & gas density power-law slope at the stagnation radius
  (eq.~[\ref{eq:densSlope}]) \\
  \hline
\label{table:definitions}  
\end{tabular}
%\begin{tablenotes}
%\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}): stellar
  wind heating ({\it orange}), Ia supernovae ({\it green}),
  millisecond pulsars ({\it blue}), and compton heating ({\it pink}).
  Each heating source varies with black hole mass $\Mbh$ calculated
  for average SFHs from \citet{MosterNaab+:2013a}; see
  Appendix~\ref{app:windheat} for details.  {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
  v_{w}^{2}$) from the top panel to the radiative cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter
  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star SFHs
  from \citealt{MosterNaab+:2013a} (blue), the ratio of Ia radius to
  stagnation radius as a function of $\Mbh$ (green), and the ratio of
  $\zeta/\zeta_{c}$ (purple), where $\zeta_c$
  (eq.~[\ref{eq:zetacrit}]) is the critical heating parameter $\zeta
  \equiv \sqrt{1+(v_w/\sigma_0)^2}$ below which outflows are
  impossible.  The latter quantity is calculated for core
  ($\Gamma=0.1$) galaxies  using mean scaling
  relations for $r_b$, $\rinf$, and $\Gamma$ from the
  \citet{LauerFaber+:2007a} galaxy sample.}
\end{figure}
